### 2014-05-30 ACL2014/abstract.tex
Updated latex files

\begin{abstract}
Many Web, Mobile, and NLP applications 
rely on finding nearest neighbors 
for a given query from a commercial large-scale query logs . 
Due to the large scale volume of queries, 
computing nearest neighbors from all queries using brute force linear 
search is a computationally time intensive task. 
To challenge the aforementioned problem, we exploit existing 
\lshf (a.k.a, \lsh) methods and propose 
their novel variants in distributed setting (e.g. Hadoop). 
Our experimental results show that couple of our 
new variants of \lsh get signiﬁcantly better recall than vanilla \lsh by 
using the same number of hash tables. 
\end{abstract}

>>>>

\begin{abstract}
Many Web, Mobile, and NLP applications 
rely on finding nearest neighbors 
for a given query from a commercial large-scale query logs . 
Due to the large scale volume of queries, 
computing nearest neighbors from all queries using brute force linear 
search is a computationally time intensive task. 
To challenge the aforementioned problem, we exploit existing 
\lshf (a.k.a, \lsh) methods and propose 
their novel variants in distributed setting (e.g. Hadoop). 
Our experimental results show that couple of our 
new variants of \lsh get significantly better recall than vanilla \lsh by 
using the same number of hash tables. 
\end{abstract}

### 2014-05-30 ACL2014/system.tex
Updated latex files

Next, we present four new variants of vanilla \lsh algorithm motivated by the research on Multi-Probe LSH \cite{LvVLDB07}. 
A signiﬁcant drawback of vanilla \lsh is the requirement for a large number of hash tables in order to achieve good recall 
in finding nearest neighbors. 
The goal of  \mblshf is to get signiﬁcantly better recall than the vanilla \lsh by using 
the same number of hash tables. The main idea behind \mblshf is to look up multiple buckets within a table that have a high probability 
of containing the nearest neighbors of a query. We present a high-level idea behind the \mblshf algorithm; 
for more details, the reader is referred to \cite{LvVLDB07}.

@@

A family is generally interesting when  $P_1>P_2$. 
However, the difference between $P_1$ and $P_2$ can be very small. 
Given a family $H$ of hash functions with parameters ($R, cR, P_1,P_2$), 
\lsh algorithm is devised by amplifying the gap between 
the two probabilities $P_1$ and $P_2$ by concatenating several functions. 
In particular, \lsh algorithm concatenates $K$ hash functions: 
$g(q)=(h_1(q),h_2(q),\dots,h_k(q))$. The larger value of $K$ leads to larger 
gap between probabilites of collision between close queries and far queries; 
the probabilities are $P_1^{K}$ and $P_2^{K}$ respectively. 
The advantage of this amplication is that now the algorithm is more precise meaning 
the probabilty of similar queries falling in same bucket is big; 
and dis-similar queries falling in same bucket is small.

@@

In this paper, we are interested in cosine similarity, and use the \lsh family defined by Charikar \shortcite{Charikar02STOC}. 
For two queries; $p,q \in \mathbb{R}^D$, the cosine similarity is $\left( \frac{p.q}{ \| p \| \| q \| }\right)$. 
The \lsh functions for cosine similarity is defined using sign($\alpha.p$); where $\alpha \in \mathbb{R}^D$ is a random vector. 
Negative sign is represented as zero and positive sign as one; hence indexes of buckets in hash tables are $K$-sized bit signatures.  
To generate $\alpha$, we exploit the prior work on 
generating random projections \cite{Achlioptas03,LiH06} and 
use hash functions trick to implictly map features ($\mathbb{R}^D$) to a set of \{-1,+1\}.
\footnote{Note, we respresent our queries ($p$ and $q$) using only non-zero features.}  
This hashing trick is important and useful as we do not need to explictly store the 
huge random projection matrix of size $D \times K \times L$.

>>>>

Next, we present four new variants of vanilla \lsh algorithm motivated by the research on Multi-Probe LSH \cite{LvVLDB07}. 
A significant drawback of vanilla \lsh is the requirement for a large number of hash tables in order to achieve good recall 
in finding nearest neighbors. 
The goal of  \mblshf is to get significantly better recall than the vanilla \lsh by using 
the same number of hash tables. The main idea behind \mblshf is to look up multiple buckets within a table that have a high probability 
of containing the nearest neighbors of a query. We present a high-level idea behind the \mblshf algorithm; 
for more details, the reader is referred to \cite{LvVLDB07}.

@@

A family is generally interesting when  $P_1>P_2$. 
However, the difference between $P_1$ and $P_2$ can be very small. 
Given a family $H$ of hash functions with parameters ($R, cR, P_1,P_2$), 
\lsh algorithm is devised by amplifying the gap between 
the two probabilities $P_1$ and $P_2$ by concatenating several functions. 
In particular, \lsh algorithm concatenates $K$ hash functions: 
$g(q)=(h_1(q),h_2(q),\dots,h_k(q))$. The larger value of $K$ leads to larger 
gap between probabilites of collision between close queries and far queries; 
the probabilities are $P_1^{K}$ and $P_2^{K}$ respectively. 
The advantage of this amplification is that now the algorithm is more precise meaning 
the probability of similar queries falling in same bucket is big; 
and dis-similar queries falling in same bucket is small.

@@

In this paper, we are interested in cosine similarity, and use the \lsh family defined by Charikar \shortcite{Charikar02STOC}. 
For two queries; $p,q \in \mathbb{R}^D$, the cosine similarity is $\left( \frac{p.q}{ \| p \| \| q \| }\right)$. 
The \lsh functions for cosine similarity is defined using sign($\alpha.p$); where $\alpha \in \mathbb{R}^D$ is a random vector. 
Negative sign is represented as zero and positive sign as one; hence indexes of buckets in hash tables are $K$-sized bit signatures.  
To generate $\alpha$, we exploit the prior work on 
generating random projections \cite{Achlioptas03,LiH06} and 
use hash functions trick to implicitly map features ($\mathbb{R}^D$) to a set of \{-1,+1\}.
\footnote{Note, we represent our queries ($p$ and $q$) using only non-zero features.}  
This hashing trick is important and useful as we do not need to explicitly store the 
huge random projection matrix of size $D \times K \times L$.
